{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-12-01 wacv_for_review.tex
last stretch.

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following function would make it more useful for
the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

In this paper, we propose a single-target tracking algorithm that does
not require offline training and can run in high-speed. Specifically, 
we would like to have our algorithm 1) learn
the appearance model of a target on the fly and 2) run on a
typical desktop as fast as $300$-$450$ fps.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rates to compare the performance of the proposed algorithm with
those of the state-of-the-art tracking algorithms. For the precision,
we rank the trackers based on the precision numbers at 20 pixels
whereas in the success rate plots, they are ranked based on the area under
curve (AUC) scores. The tracking algorithms under the comparison
include ones in high-speed ($\geq$300 fps): KCF
\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
\cite{zhang2014fast} and ones in relatively lower-speed ($\leq$50):
ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
convolutional features, however, to perform fair comparison, we employ
fHoG and color-naming features similar to our tracker. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
{\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
at 20 pixels precision. In particular, three algorithms, SAMF,
DSST, and Struck did about $5\%$ better than ours in accuracy, but
10-20 times slower. The more recent trackers, ECO and CCOT, on the
other hand, outperforms {\it E}nKCF by $15\%$ while running at
10-15 times slower. For the scale adaptation, {\it E}nKCF did
fourth best in terms of AUC for the success rate plot. It
outperformed other high-speed trackers by about $20\%$-$25\%$ in
AUC. In addition, it performed even better than some of the
lower-speed trackers.  For example, for AUC, {\it E}nKCF
outperformed Struck and DSST by $5\%$ and $10\%$ while running at
more than $10$ and $30$ times faster. 
\textit{YoungWoo : Does the following part make sense to you?}
The DSST assigns a 1-D scale filter and searches over 33 candidates in the scale pool whereas the {\it E}nKCF
uses a 2-D scale filter and 3 candidates. Although the DSST searches for the scale in a larger search space, the {\it E}nKCF
achieves higher AUC. We believe this can be due to two reasons. First, the DSST's 1-D scale filter lacks spatial information about
the target. Second, the DSST scale filter employs only fHoG whereas the {\it E}nKCF uses both color-naming and fHoG features
in the scale filter.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
how the frame rate of a testing video would affect the performance of
a tracking algorithm. To this end, we use the temporarily down-sampled version
of the UAV123, called UAV123$\_$10fps dataset. We believe the downsampling
would make the original UAV123 data more challenging because the
displacements of the moving objects become even bigger. To tackle this challenge, we 
slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
removed the particle filter due to larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET}
shows the performance of the modified version of {\it E}nKCF and other
tracking methods. The precision rates of the ECO and CCOT dropped
about $10\%$ in comparison to the original UAV123 dataset. Our tracker
outperforms other high-speed correlation filter based trackers
including KCF, DSST by about $15\%$-$20\%$ and showed a precision rate
similar to that of SAMF. It ranks as fourth in AUC while running about
$10$ to $100$ times faster than the top three trackers. 
\textit{YoungWoo : I did not get this part clearly. How sensitive the frame rate 
or how sensitive the tracker is
?} It was interesting to observe how sensitive the frame rate is to the
performance of the state-of-the-art tracking algorithms, and, with a
slight modification, the proposed method effectively handled large
displacement of objects in successive frames. 
\textit{YoungWoo : I also believe that we should emphasize how the state-of-the-art
trackers perform in lower frame rates. And I believe this is what this paper \cite{mueller2017context}
says. They rank the trackers by evaluating them on videos matching their fps. I was thinking of running 
ECO and CCOT in UAV123 in 5 fps videos and mention how they degrade with respect to the decreasing fps.
I believe this is our contribution and we should emphasize it.}

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on a lower frame rate
  data.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. Among other practical considerations, it would be
desirable if such computer vision algorithms require no offline
training and operate at high-speed. To develop a single-target
tracking algorithm to meet these features, we proposed an extension
of KCF that applies three KCFs, in turn, to address the variations in
scale and translation of moving objects. We also developed a particle
filter to smooth the transition between three KCFs, especially the
transition between the scale and large ROI translation filter. Through
experiments, it was found that the way the {\it E}nKCF deployed three KCFs
was optimal and the particle filter contributed to boost the
performance in the existence of noise. 
We used two public datasets to evaluate the performance
of the proposed algorithm and other state-of-the-art tracking
algorithms, and found that, on average, the performance of the
proposed algorithm is better than other high-speed trackers over 5\%
on precision at 20 pixels and 10-20\% on AUC. Our implementation ran
at 340 fps for OTB100 and at 416 fps for UAV123 data that is faster
than DCF (292 fps) for OTB100 and KCF (292 fps) for UAV123. Finally,
we explored the idea of utilizing deep features for the proposed
algorithm and found that the deep features helped the proposed
algorithm boost the performance by $10\%$.

As future work, we would like to investigate a way of re-initializing
a target when the target is lost, due to occlusion, illumination
change, drastic camera motion, etc.

>>>>

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following function would make it more useful for
the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others. To this end, in this paper, we propose a single-target
tracking algorithm that does not require offline training and can run
in high-speed. Specifically, we would like to have our algorithm 1)
learn the appearance model of a target on the fly and 2) run on a
typical desktop as fast as $300$-$450$ fps.

@@

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rates to compare the performance of the proposed algorithm
with those of the state-of-the-art tracking algorithms. For the
precision, we rank the trackers based on the precision numbers at 20
pixels whereas in the success rate plots, they are ranked based on the
area under curve (AUC) scores. The tracking algorithms under the
comparison include ones in high-speed ($\geq$300 fps): KCF
\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
\cite{zhang2014fast} and ones in relatively lower-speed ($\leq$50):
ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
convolutional features, however, to perform fair comparison, we employ
fHoG and color-naming features similar to our tracker. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
    {\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
    at 20 pixels precision. In particular, three algorithms, SAMF,
    DSST, and Struck did about $5\%$ better than ours in accuracy, but
    10-20 times slower. The more recent trackers, ECO and CCOT, on the
    other hand, outperforms {\it E}nKCF by $15\%$ while running at
    10-15 times slower. For the scale adaptation, {\it E}nKCF did
    fourth best in terms of AUC for the success rate plot. It
    outperformed other high-speed trackers by about $20\%$-$25\%$ in
    AUC. In addition, it performed even better than some of the
    lower-speed trackers.  For example, for AUC, {\it E}nKCF
    outperformed Struck and DSST by $5\%$ and $10\%$ while running at
    more than $10$ and $30$ times faster. For the DSST, we believe our
    algorithm outperformed it because, first of all, the DSST uses a
    1-D scale filter and searches the target's scale over 33
    candidates in a scale pool whereas our algorithm uses a 2-D scale
    filter with 3 candidate scales. Learning a 2-D filter would result
    in learning more spatial information. Second of all, the DSST use
    only fHoG whereas our algorithm uses both fHoG and color-naming
    features. Learning more features, not for always, but would
    provide better understanding on the ROI.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
how the frame rate of a testing video would affect the performance of
a tracking algorithm. To this end, we use the temporarily down-sampled
version of the UAV123, called UAV123$\_$10fps dataset. We believe the
downsampling would make the original UAV123 data more challenging
because the displacements of the moving objects become even bigger. To
tackle this challenge, we slightly modified the proposed algorithm --
ran $R_{t}^{L}$ every frame and removed the particle filter due to
larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET} shows the
performance of the modified version of {\it E}nKCF and other tracking
methods. The precision rates of the ECO and CCOT dropped about $10\%$
in comparison to the original UAV123 dataset. Our tracker outperforms
other high-speed correlation filter based trackers including KCF, DSST
by about $15\%$-$20\%$ and showed a precision rate similar to that of
SAMF. It ranks as fourth in AUC while running about $10$ to $100$
times faster than the top three trackers. It was interesting to
observe how sensitive the performance of the state-of-the-art tracking
algorithms is the frame rate, and, with a slight modification, the
proposed method effectively handled large displacement of objects in
successive frames.
\begin{comment}
\textit{YoungWoo : I also believe that we should
  emphasize how the state-of-the-art trackers perform in lower frame
  rates. And I believe this is what this paper
  \cite{mueller2017context} says. They rank the trackers by evaluating
  them on videos matching their fps. I was thinking of running ECO and
  CCOT in UAV123 in 5 fps videos and mention how they degrade with
  respect to the decreasing fps.  I believe this is our contribution
  and we should emphasize it.

  Burak: To be honest with you, it's a cheating -- we modified our
  algorithm to make it work better, but didn't do anything or
  modifications to other algorithms. Yes, all other algorithms didn't
  perform well on a low frame rate, but it was a unfair comparison. So
  I wouldn't think it's a contribution.  }
\end{comment}
\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on a lower frame rate
  data.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. Among other practical considerations, it would be
desirable if such computer vision algorithms require no offline
training and operate at high-speed. To develop a single-target
tracking algorithm to meet these features, we proposed an extension of
KCF that applies three KCFs, in turn, to address the variations in
scale and translation of moving objects. We also developed a particle
filter to smooth the transition between three KCFs, especially the
transition between the scale and large ROI translation filter. Through
experiments, we found that the way the {\it E}nKCF deployed three KCFs
was optimal, and the particle filter contributed to increase the
performance.  We used two public datasets to evaluate the performance
of the proposed algorithm and other state-of-the-art tracking
algorithms, and found that, on average, the performance of the
proposed algorithm is better than other high-speed trackers over 5\%
on precision at 20 pixels and 10-20\% on AUC. Our implementation ran
at 340 fps for OTB100 and at 416 fps for UAV123 data that is faster
than DCF (292 fps) for OTB100 and KCF (292 fps) for UAV123. Finally,
we explored the idea of utilizing deep features for the proposed
algorithm and found that the deep features helped the proposed
algorithm boost the performance by $10\%$.

Although the proposed algorithm showed a promising result tested with
challenging data, we believe the corner case analysis has not been
extensively done yet. As future work, we would like to thoroughly
study when and what conditions our algorithm would fail to track
moving objects. In addition, we also would like to investigate a way
of re-initializing a target when the target is lost, due to occlusion,
illumination change, drastic camera motion, etc.
